---
title: "Alcohol vs Seat choice"
author: "Cesar Guillen"
date: "Summer 2022"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r include=FALSE}
require(tidyverse)
require(tigerstats)
davisdata <- read.csv(file="UCDavis.csv")
```
## Our Goal is to answer this question Is there a difference between the alcohol consumed between the row
## you choose to sit in??

## Now with ggplot - first select the basic data

```{r}
basicCN <- ggplot(davisdata,aes(y=alcohol,x=Seat))
```
## Now add in boxplot

```{r}
basicCN + geom_boxplot()
```
  
  
### get fancy  

```{r}
basicCN + geom_boxplot(notch=TRUE,outlier.color = "red") + stat_boxplot(geom ='errorbar') + labs(title="Fancy notch boxplot \n with 2 lines")
```

Those who sit in the back rows seem to consume more alcohol than those who sit in the middle and front rows of the stadium. Which could mean that the more father back your seats are in a stadium the more alcohol you are likely to consume.  


## Numerical Summarys 

```{r}
favstats(alcohol~Seat,data=davisdata) 
```

## Inferential Tests

## Conclusions


